First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-08-29 eg6-letters/coherent/dvcs_he4_prl.tex
Started answer to the PRL referees

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model-dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is is due to $\alpha_2$ being much smaller than $\alpha_1$ in
Eq.~(\ref{eq:A_LU-coh}). While the precision of this measurement is not at a
sufficient level to discriminate between the models, these results demonstrate
the possibility of extracting the CFF of a spin-0 target directly from a $A_{LU}$
measurement.

>>>>

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the $A_{LU}$ is possible without model-dependent assumptions beyond
leading-twist and leading-order dominance. The amplitude and the dependencies 
observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is due to $\alpha_2$ being much smaller than $\alpha_1$ in
Eq.~(\ref{eq:A_LU-coh}). While the precision of this measurement is not at a
sufficient level to discriminate between the models, these results demonstrate
the possibility of extracting the CFF of a spin-0 target directly from a $A_{LU}$
measurement.
